\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, hyperref}

\title{Photon as a Pure Information Carrier}
\author{Krzysztof Włodzimierz Banasiewicz \\\\ Independent Researcher, The Hague / Wrocław}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
In this note we argue that the photon, despite having zero rest mass, 
should be understood as the fundamental carrier of information in the quantum universe. 
While massive particles embody structured and stored information, photons transmit 
pure information encoded in energy, frequency, and quantum correlations. 
This interpretation emerges naturally when combining relativity, quantum mechanics, 
and the informational perspective on physics.
\end{abstract}

\section{Introduction}
It is a well established result that the photon has vanishing rest mass:
\begin{equation}
m_0(\gamma) = 0.
\end{equation}
Yet photons carry energy and momentum,
\begin{equation}
E = h\nu, \quad p = \frac{E}{c},
\end{equation}
which makes them gravitationally relevant. Light increases the mass of black holes, 
deflects in gravitational fields, and mediates the electromagnetic force.

\section{Rest Mass vs. Relativistic Mass}
In special relativity, the concept of ``relativistic mass'' is defined as
\begin{equation}
m_{rel} = \frac{E}{c^2}.
\end{equation}
From this viewpoint, the photon can be assigned an effective mass proportional 
to its energy. This reconciles the massless nature of the photon at rest 
with its physical influence in motion.

\section{Photon as Information Carrier}
Landauer's principle establishes a minimum energy cost for one bit of information:
\begin{equation}
E_{bit} = k_B T \ln 2.
\end{equation}
If energy is information, then the photon --- as a quantum of electromagnetic energy ---
represents the most elementary packet of transmitted information.
Unlike massive particles, which encode information in persistent structures 
(quantum states bound by interactions), photons encode and deliver 
information in transit.

\section{Quantum Correlations and Entanglement}
Beyond carrying energy, photons transmit entanglement.
They are natural messengers of quantum correlations, 
establishing nonlocal links across spacetime. 
This makes them both the carriers of classical signals 
and the qubits of quantum networks.

\section{Conclusion}
The photon is unique among particles: it has no rest mass, yet it carries 
energy, momentum, and information. 
In the informational interpretation of physics, massive particles 
are repositories of structured information, whereas the photon is a 
pure information carrier --- the messenger of the quantum universe.

\end{document}
